% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file.

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
%\documentclass[letterpaper,twocolumn,10pt]{article}
\documentclass[10pt,preprint]{sigplanconf}
\usepackage{subcaption}
\usepackage{graphicx}
%\usepackage[demo]{graphicx} % omit 'demo' for real document
\usepackage[normalem]{ulem}
\usepackage{multirow}    % Use to create table with a column that spans multiple rows
\usepackage{pifont}      % Provides the ding symbol used for comments
\usepackage{xcolor}       % Used to highlight comments
\usepackage{xspace}      % Intelligently adds space after a word via \xspace
\usepackage{flushend}    % balance the last page
\usepackage{upgreek}

\usepackage{times}
\usepackage{datetime}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={blue!80!black}
}


\conferenceinfo{SOSP'15}{October 4--7, 2015, Monterey, CA}
\copyrightyear{2015} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

\begin{document}

\newcommand{\name}{PTCache\xspace}
\newcommand{\eat}[1]{}  %% for quick commenting of a large trunk of texts
\newcommand{\authcomment}[3]{\textcolor{#3}{#1 says: #2}}\newcommand{\yueqiang}[1]{\authcomment{Yueqiang}{#1}{red}}
\newcommand{\zhi}[1]{\authcomment{Zhi}{#1}{red}}



%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
%\title{\Large \bf Improving I/O Performance of All Peripheral Devices on Paravirtualized Platforms}
\title{\Large \bf PTCache: Page Table Management Improvements For Performance Benefits }

\authorinfo{Anonymous}{}

\maketitle
% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
%\thispagestyle{empty}


\begin{abstract}
%As a key virtualization technique, the paravirtualization technique is widely applied to many existing cloud platforms.
When the mainstream operating systems, such as Linux, move onto the paravirtualized platforms, their page table management components are required to be properly patched.
However, the existing updates mainly focus on the security enhancements, without enough attentions for the performance improvements.
Based on our observations, there are two main performance issues.

The first one is the additional dependence between the page table (de)allocations and the IOTLB flushes, which inevitably introduces extra IOTLB misses, and would consequently have negatively impacts on the I/O performance of all peripheral devices.
The other one is the long execution paths for page table allocations and deallocations, which directly leads to the operating time of the page table creations and destructions, and consequently increases the latency of the creations and exits of processes.


In this paper, we propose Page-Table Cache (\name), a novel software-only approach for improving the performance in page table management.
First, \name eliminates the additional IOTLB misses with a fine-grained validation scheme, which separates the DMA and software validations, instead of doing them all in one.
Second, \name reduces the length of the execution path of the page table (de)allocations by a page table cache, which maintains a dedicated buffer for serving page table allocations and deallocations.
We implement a prototype on Xen with Linux as the guest VM's kernel. We do small modifications of Xen version 4.2.1 ($166$ SLoC) and Linux kernel version 3.2.0 ($350$ SLoC).
We evaluate the I/O performance in both micro and macro ways.
The micro experiment results indicate that \name is able to effectively eliminates the additional IOTLB misses, from xxx to zero, and reduces the page table (de)allocations, (xx\%, xx\%), (xx\%, xx\%) and (xx\%, xx\%) improvements for allocation and deallocation pairs for three-levels page table, from top to bottom.
The macro benchmarks shows that the latencies of the processes creation and exit are reduced as expected, from xx\% to xx\% on average.

\zhi{When mainstream operating systems such as Linux provide paravirtualization support, contemporary patches to the management components of guest page tables mainly satisfy the security requirements while without having paid enough attentions to the performance improvements, resulting in two noticeable issues as follows. Coming first is the long execution paths for page table allocations and deallocations, badly affecting the creations and exits of processes. The other one is an additional dependence between the page table (de)allocations and the IOTLB flushes, which inevitably introduces extra IOTLB misses, thus causing negative impacts on the I/O performance of all peripheral devices. In this paper, we propose Page-Table Cache (\name), a novel software-only approach for improving the performance in the page table management. First, \name shortens the length of the page table (de)allocations-path by a page table cache, which maintains a dedicated cache to serve the page table (de)allocations. Second, \name eliminates the additional IOTLB misses with a fine-grained validation scheme, which separates MMU and IOMMU page table updates, instead of completing both updates in once as before. And the scheme is also helpful to facilitate the (de)allocations of page tables. We implement a prototype on Xen with Linux as the guest VM's kernel with small modifications of Xen version 4.2.1 (xxx SLoC) and Linux kernel version 3.2.0 (xxx SLoC). We evaluate the performance in both micro and macro ways. The micro experiment results indicate that \name is able to effectively eliminates the additional IOTLB flushes, from xxx to zero, and benefits the page table (de)allocations, (xx\%, xx\%), (xx\%, xx\%) and (xx\%, xx\%) improvements for allocation and deallocation pairs of three-level page table, from top level to bottom. The macro benchmarks show that \name brings no bad effect on system performance and efficiently facilitates processes creations and exits by xx\% on average.}
\end{abstract}
\category{CR-number}{subcategory}{third-level}

% general terms are not compulsory anymore, 
% you may leave them out
\terms
term1, term2

\keywords
keyword1, keyword2

\input{intro.tex}
\input{background.tex}
\input{motivation.tex}
\input{prob.tex}
%\input{rationale.tex}
\input{overview.tex}
\input{implementation.tex}
\input{evaluation.tex}
\input{discussion.tex}
%\input{related.tex}
%\input{conclusion.tex}

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}




%Now we get serious and fill in those references.  Remember you will
%have to run latex twice on the document in order to resolve those
%cite tags you met earlier.  This is where they get resolved.
%We've preserved some real ones in addition to the template-speak.
%After the bibliography you are DONE.

%{\footnotesize \bibliographystyle{acm}
%\bibliography{../common/bibliography}}
{
%\footnotesize
\bibliographystyle{plain}
\bibliography{fastio}
}


\end{document}

IOMMUs have been pervasively deployed on paravirtualized systems for the protection of the hypervisor and the security-critical data structures, e.g., the shared page tables. According to our observations, certain updates of the guest VM's page tables that are supposed to be orthogonal to the device I/O performance, would surprisingly lead to a large number of IOTLB misses. It implies that the I/O performance of all peripheral devices will be affected by the seemingly unrelated guest page table updates. Unfortunately, no existing work uncovers this dependency and adjusts the design of the paravirtualized hypervisor and the guest operating system.







