%\documentclass[letterpaper,twocolumn,10pt]{article}
\documentclass[pageno]{jpaper}

%replace XXX with the submission number you are given from the ASPLOS submission site.
\usepackage[normalem]{ulem}
\usepackage{usenix,epsfig,endnotes,array}
\usepackage{multirow}    % Use to create table with a column that spans multiple rows
\usepackage{pifont}      % Provides the ding symbol used for comments
\usepackage{color}       % Used to highlight comments
\usepackage{xspace}      % Intelligently adds space after a word via \xspace

\begin{document}
\newcommand{\asplossubmissionnumber}{xxx}
\newcommand{\mypara}[1]{\vspace{2pt}\noindent\textbf{{#1. }}}
\newcommand{\name}{IOSUP\xspace}
\newcommand{\eat}[1]{}  %% for quick commenting of a large trunk of texts

\newcommand{\authcomment}[3]{\ding{110}\ding{43}\textcolor{#3}{#1 says: #2}}
%\newcommand{\authcomment}[3]{\textcolor{#3}{#1 says: #2}}
%\newcommand{\authcomment}{}
\newcommand{\yueqiang}[1]{\authcomment{Yueqiang}{#1}{red}}
\newcommand{\zhi}[1]{\authcomment{Zhi}{#1}{red}}
\newcommand{\junqing}[1]{\authcomment{Junqing}{#1}{red}}


%don't want date printed
\date{}

%make title bold and 14  pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Improving I/O Performance of All Peripheral Devices on Paravirtualized Platforms}


%for single author (just remove % characters)
\author{
{\rm Anonymous}
}% end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}


\subsection*{Abstract}
IOMMUs have been pervasively deployed on paravirtualized systems for the protection of the hypervisor and the security-critical data structures, e.g., the shared guest page tables. According to our observations, the updates of the guest page tables that are supposed to be orthogonal to the device I/O performance, would surprisingly lead to a large numbers of IOTLB misses. It implies that the I/O performances of all peripheral devices will be affected by the seemingly unrelated guest page table updates. Until now, researchers and developers are not aware of the existence of this dependence and do not consequently adjust the design of the paravirtualized hypervisor and the guest operating systems.

In this paper, we are the first one to deeply demonstrate the impact upon the device I/O performance due to the page table updates. To minimize the impact, we propose \name(I/O Speed-UP), a novel software-only approach for decreasing the IOTLB misses, as well as retaining the security of hypervisor.
We also implement an prototype on Xen and Linux kernel. We do small modifications of Xen (xxx SLoC) and Linux kernel version 3.2.0 (xxx SLoC). We also evaluate the I/O performance in both micro and macro ways. The micro experiment results indicate that the new algorithm is able to effectively reduce the miss rate of IOTLB with even less CPU usage, especially when the page tables are frequently updated. The macro benchmarks shows that the I/O devices always produce better (or the same) performance, especially when the system frequently generate many temporal processes.


\input{intro.tex}
%\input{preliminary.tex}
\input{prob.tex}
%\input{rationale.tex}
%\input{overview.tex}
%\input{imple.tex}
%\input{evaluation.tex}
%\input{discussion.tex}
%\input{related.tex}
%\input{conclusion.tex}

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
{
%\footnotesize 
\bibliographystyle{plain}
\bibliography{iosup}
}
%\bibliographystyle{acm}
%\bibliographystyle{splncs}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%

\end{document}
